Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-02 paper/paper.tex

>>>>

\begin{mdframed}
  \vspace{1em}
  \textbf{Box 2: Hypotheses for testing the MDP account of DMN function}
\begin{enumerate}
\item Experiment (Humans): We hypothesize a functional relationship between the DMN closely associated with the occurrence of stimulus-independent thoughts and the reward circuitry. During an iterative neuroeconomic two-player game, fMRI signals in the DMN could be used to predict reward-related signals in the nucleus accumbens across trials in a continuous learning paradigms. We expect that the more DMN activity is measured to be increased, supposedly the higher the tendency for stimulus-independent thoughts, and the more the fMRI signals in the reward circuits should be independent of the reward context
in the sensory environment.

\item Experiment (Humans): We hypotherize that time horizon should be modulated by different factors such as age, stress, and impulsivity. Using a temporal discounting task, we can measure how the time horizon could be affected at the behavioral level, and then trace back its potential representation at the neural level. Experimental design can be between groups (by age or with a impulsive population like chronic gamblers or drug addicts), or within group using a stress.

% To exam-ine this question, Fellows and Farah (2005) investigated the effects of dorsolateral frontal (DLF) and ventromedial frontal (VMF) lobe damage on two aspects of temporal foresight—namely, temporal discounting and the futuretime perspective (measuredby an adaptation of Wallace’s [1956] list of future life events).

\item Experiment (Animals): how synaptic epigenesis between DMN nodes can form a neural correlate of the policy matrix update? % Simulations:
